### 2022-03-08 manuscript.tex
tiff [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/6d999790895a2c1e1221abb5b70c9b11f5d4b2e5.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/6d999790895a2c1e1221abb5b70c9b11f5d4b2e5/checks
https://github.com/scherzerthesis/thesis/actions/runs/1952064417

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/852523248b1b0d8eaf8ca6a0e57ff961b5320e2e/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/852523248b1b0d8eaf8ca6a0e57ff961b5320e2e}{scherzerthesis/thesis@8525232}
on March 7, 2022.

@@

@@

Results

@@

Given our findings of SETD2 loss increased tumor burden concurrent with BRAF(V600E) we next validated SETD2 in a new cohort of mice with single-guide RNAs targeting SETD2. Indeed, loss of SETD2 increased tumor burden from 5\% to over 30\% in some animals. Since SETD2 antibodies are unreliable in both western blots and immunohistochemistry we used H3K36me3 as a surrogate marker for SETD2 activity by immunohistochemistry. Whereas 90\% of nuclei in BRAF (V600E) only tumors were H3K36me3, more than 60\% tumors of mice infected with SETD2 CRISPR virus were negative for H3K36me3. Furthermore, when classified by H3K36me3-positive or -negative, there is even stronger evidence that SETD2 loss leads to larger tumor formation.

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/tubaseq_figure1.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:06}
}
\end{figure}

@@

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure1_021022.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/6d999790895a2c1e1221abb5b70c9b11f5d4b2e5/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/6d999790895a2c1e1221abb5b70c9b11f5d4b2e5}{scherzerthesis/thesis@6d99979}
on March 8, 2022.

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{results}{%
\section{Results}\label{results}}

@@

Given our findings of SETD2 loss increased tumor burden concurrent with BRAF(V600E) we next validated SETD2 in a new cohort of mice with single-guide RNAs targeting SETD2. Indeed, loss of SETD2 increased tumor burden from 5\% to over 30\% in some animals. Since SETD2 antibodies are unreliable in both western blots and immunohistochemistry we used H3K36me3 as a surrogate marker for SETD2 activity by immunohistochemistry. Whereas 90\% of nuclei in BRAF (V600E) only tumors were H3K36me3, more than 60\% tumors of mice infected with SETD2 CRISPR virus were negative for H3K36me3. Furthermore, when classified by H3K36me3-positive or -negative, there is even stronger evidence that SETD2 loss leads to larger tumor formation

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tiff}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tiff}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tiff}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tiff}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba5.tiff}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

\begin{figure}
\hypertarget{fig:06}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/tuba1.tiff}
\caption{\textbf{This is the title of Figure} this is the text.}\label{fig:06}
}
\end{figure}

@@

\hypertarget{introduction-1}{%
\subsection{Introduction}\label{introduction-1}}

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

\begin{figure}
\hypertarget{fig:11}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/figure.svg}
\caption{\textbf{Differential BRAF\textsuperscript{V600E} lung tumorigenesis imparted by p53-Hotspot mutants.} \textbf{(A)} Genetically-engineered alleles of \emph{Braf\textsuperscript{v600E}} and \textsuperscript{Trp53} before and after Cre-Recombinase. \textbf{(B)} Tumor burden and \emph{(C)}** Tumor size of BRAF(V600E) plus Trp53-wildtype, null, or mutant alleles 14 weeks post Cre-mediated recombination. \emph{(D)} Representative H\&E images 14 weeks after Cre-recombination. \textbf{(E)} Survival of mice with Heterozygous \emph{Trp53} mutant alleles. \textbf{(F)} Survival of mice with homozygous \emph{Trp53} alleles.}\label{fig:11}
}
\end{figure}

@@

\hypertarget{discussion-1}{%
\subsection{Discussion}\label{discussion-1}}
